
---
title: "Exercise #6"
subtitle: "Fortgeschrittene Statistische Software für NF"
author: "Frieda Krois (12745035)"
date: "`r Sys.Date()`"
output: distill::distill_article
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

My R Package "allbushelper" containing three functions is a quick start for social scientists working with the ALLBUS dataset. In this case the data needs to be downloaded already before starting the allbushelper load function (ALLBUS data isn’t publicly available via a direct URL). As a social scientist I regularly use the ALLBUS dataset and thought of a straight forward way to make initial steps (like loading, summary, first plot) easier. Maybe that will convince more Sociology Students work with R instead of STATA. 

My package can be found on a public github repository: https://github.com/Friedikr/allbushelper.


## load my newly created r package to use following functions
```{r}
library(allbushelper)
```

## load ALLBUS (needs to be downloaded from the gesis website first!)
```{r}
data <- load_allbus("ZA8831_v1-2-0.dta") # data has 5246 rows and 579 columns
```

## The dataset is big. Let's get a summary of the ALLBUS data for a better overview.
```{r}
summary_allbus(data)  # data has 5246 rows and 579 columns
```

## get a first insight of ALLBUS by plotting the eastwest variable 
```{r}
plot_eastwest(data)
```

## Submission: install package from github
```{r}
# getOption("repos") # specify the CRAN-Server
remotes::install_github("Friedikr/allbushelper") 
